Applying Radial Basis Function Networks and Markov Chains for on-line detection of concept drift in non-stationary environments

### 2019-10-30 tex/article/article.tex
Abstract fit in one page with keywords
introduction done

\begin{abstract}
The volume of data produced by computer systems has grown sharply in recent decades.
A significant part of this volume is generated as uninterrupted and potentially infinite sequences known as data streams.
Usually, these streams are produced by non-stationary environments, in which the data distribution can change over time.
Systems applied to these environments may not be able to adapt to the new distribution, consequently deteriorating their performance.
In the literature, this phenomenon is named as concept drift.
%
Nevertheless,
most concept drift detection methods are unsuited for non-stationary environments with data streams,
because these algorithms often require the correct labeling of data or do not match the strict response time and resource usage requirements.
%
In this context, this paper proposes a novel proactive on-line concept drift detection method, called RBFChain.
The proposed method relies on Radial Basis Function Networks implicit clustering property and uses Markov Chains to model the transitions.
%
To assess RBFChain as a viable concept drift detector,
an analysis of sensitivity, accuracy,
and noise tolerance was performed using synthetic datasets,
and results were compared to the main algorithms found in the literature.
%
Furthermore, the technique was applied to the real-world problem of eye-tracking:
a critical issue in different areas of knowledge,
since many behavioral experiments use eye-tracking information as a relevant analysis factor.
%
Experimental results suggest that RBFChain is statistically better or equivalent to other detectors as it offers greater or equal overall classification accuracy with synthetic datasets.
Besides, the algorithm showed to apply to the eye monitoring problem, as it was able to classify fixations and saccades in real-time with accuracy comparable to state of the art.
\end{abstract}

@@

Experimental results suggest that RBFChain is statistically better or equivalent to other detectors as it offers greater or equal overall classification accuracy with synthetic datasets.
Besides, the algorithm showed to apply to the eye monitoring problem, as it was able to classify fixations and saccades in real-time with accuracy comparable to state of the art.

>>>>

\begin{abstract}
The volume of data produced by computer systems has grown sharply in recent decades.
A significant part of this volume is generated as uninterrupted and potentially infinite sequences known as data streams.
Usually, these streams are produced by non-stationary environments, in which the data distribution can change over time.
Systems applied to these environments may not be able to adapt to the new distribution, consequently deteriorating their performance.
In the literature, this phenomenon is named as concept drift.
%
Nevertheless,
most concept drift detection methods are unsuited for non-stationary environments with data streams,
because these algorithms often require the correct labeling of data or do not match the strict response time and resource usage requirements.
%
In this context, this paper proposes a novel proactive on-line concept drift detection method, called RBFChain.
The proposed method relies on Radial Basis Function Networks implicit clustering property and uses Markov Chains to model the transitions.
%
To assess RBFChain as a viable concept drift detector,
an analysis of sensitivity, accuracy,
and noise tolerance was performed using synthetic datasets,
and results were compared to the main algorithms found in the literature.
%
Furthermore, the technique was applied to the real-world problem of eye-tracking:
a critical issue in different areas of knowledge,
since many behavioral experiments use eye-tracking information as a relevant analysis factor.
%
Experimental results with synthetic datasets suggest that RBFChain is statistically better or equivalent to other detectors.
Besides, the algorithm showed to apply to the eye monitoring problem, as it was able to classify fixations and saccades in real-time with accuracy comparable to state of the art.
\end{abstract}

@@

Experimental results with synthetic datasets suggest that RBFChain is statistically better or equivalent to other detectors as it offers greater or equal overall classification accuracy.
Besides, the algorithm showed to apply to the eye monitoring problem, as it was able to classify fixations and saccades in real-time with accuracy comparable to state of the art.
